---
title: "ice_gn"
author: "Chris R"
date: "5/24/2024"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(mgcv)
library(arrow)
library(gratia)
library(magick)
library(cowplot)
library(mnsentinellakes) #https://github.com/mnsentinellakes/mnsentinellakes
select <- dplyr::select
options(scipen = 999)
set.seed(1024)

early.anomaly = -17.52
late.anomaly = 14

rmvn <- function(n, mu, sig) { ## MVN random deviates 
    L <- mroot(sig);
    m <- ncol(L); 
    t(mu + L %*% matrix(rnorm(m * n), m, n)) 
}
```


# Read in some ice data
```{r}
ice_off <- read.csv("./data/ice_off_summarized.csv") %>% mutate(lake.id = DOW)

long_term <- ice_off %>% group_by(DOW) %>% count() %>% filter(n >= 100)

# Calulate average ice off long term
average <- ice_off %>% dplyr::filter(DOW %in% long_term$DOW) %>% 
  filter(year <= 1970) %>%
  group_by(DOW) %>% summarise(mean_ice_off = mean(min_ice_off_julian))

anomaly <- average %>% merge(ice_off, by = "DOW") %>% filter(year > 1970) %>%
  mutate(anomaly =  min_ice_off_julian - mean_ice_off) %>%
  group_by(year) %>%
  summarize(ice_off_anomaly = mean(anomaly), 
            sd_anomaly = sd(anomaly))

long_ice <- ice_off %>% group_by(DOW) %>% 
  count() %>% filter(n > 50)
```


# Model data prepared
```{r}
gn_spatial <- read.csv("./data/gillnet_aged_lake_year.csv") %>%
  mutate( lake.id = as.numeric(as.character(lake.id)),
    lake.id = fixlakeid(ifelse(lake.id == "73020002", "73020000", lake.id)),
    birth.year = year - est.age,
    year_class = as.factor(str_c(lake.id, birth.year)),
    year_f = as.factor(year), 
    birth.year = year - est.age,
    age_f = as.factor(est.age))


# Year specific ice anomaly (not lake-year specific)
walleye_anomaly_ice <- gn_spatial %>%
  merge(y = anomaly, by.x = "birth.year", by.y = "year") %>%
  filter(est.age >= 2) %>%
  filter(est.age < 13) %>%
  select(lake.id, lake.name, year, birth.year, est.age, sampling.method, 
         total.effort.1, count, cpue, 
         ice_off_anomaly, x, y, acres, shore_mi, non.fry, year_f, jd, effort.ident) %>%
  mutate(non.fry = ifelse(is.na(non.fry), 0, non.fry),
         lake.id = as.factor(lake.id)) %>%
  filter(non.fry <= 1) 
```


# Characteristics of dataset
```{r}
walleye_anomaly_ice %>% group_by(lake.id, year) %>% count()
# number of rows = number of surveys
min(walleye_anomaly_ice$year); max(walleye_anomaly_ice$year)

length(unique(walleye_anomaly_ice$lake.id)) # Number of lakes surveyed = 751
length(unique(walleye_anomaly_ice$effort.ident)) # Number of total surveys = 3913

surveys_per_lake <- walleye_anomaly_ice %>% group_by(lake.id, year) %>% count() %>% group_by(lake.id) %>% count()
median(surveys_per_lake$n)
```


# Factor smooth by age
```{r}
walleye_anomaly_ice <- gn_spatial %>%
  mutate(lake.id = mnsentinellakes::fixlakeid(lake.id)) %>%
  merge(y = anomaly, by.x = "birth.year", by.y = "year") %>%
  select(lake.id, lake.name, birth.year, sampling.method, total.effort.1, 
         est.age, count, cpue, ice_off_anomaly, x, y, acres, 
         shore_mi, non.fry, year, year_f, jd,  effort.ident) %>%
  mutate(log_acres = log(acres), 
         lake.id = as.factor(as.character(lake.id)),
         year_f = as.factor(as.character(year_f)), 
         age_f = as.factor(est.age), 
         non.fry = ifelse(is.na(non.fry), 0, non.fry),) %>%
  filter(non.fry <= 1) %>%
  filter(est.age >= 2) %>%
  filter(est.age < 13)

# https://stats.stackexchange.com/questions/637423/conceptual-interpretation-of-bs-fs-and-by-term-in-gam
# Model GS
gn.ice.gam <- gam(count ~ s(ice_off_anomaly) + 
                        s(ice_off_anomaly, age_f, bs = "fs") + s(x, y) + 
                        s(jd) + s(log(acres)) +
                    s(lake.id, bs = "re") + s(year_f, bs = "re") + offset(log(total.effort.1)), 
                  family = nb(link = "log"), method = "fREML", data = walleye_anomaly_ice)
k.check(gn.ice.gam)
appraise(gn.ice.gam)
summary(gn.ice.gam) # Deviance explained = 48
draw(gn.ice.gam, select = 1)
draw(gn.ice.gam, select = 2)

write_rds(gn.ice.gam, "./models/gillnet.recruitment.anomaly.gam.rds")
gn.ice.gam <- read_rds("./models/gillnet.recruitment.anomaly.gam.rds")
```

# Plot panel C of Fig 3
```{r}
summarized_data <- walleye_anomaly_ice %>%
  summarize(mean_log_acres = mean(log_acres), mean_x = mean(x), mean_y = mean(y),
            mean_jd = mean(jd), mean_effort = mean(total.effort.1))

pred.df = data.frame(
  ice_off_anomaly = seq(-18, 16, by = 0.5),
  age_f = rep(2:12, each = 69),
  jd = summarized_data$mean_jd, acres = summarized_data$mean_log_acres,
  lake.id = "01006200", year_f = 2011, 
  x = summarized_data$mean_x, y = summarized_data$mean_y,
  total.effort.1 = summarized_data$mean_effort) %>%
  mutate(row = row_number(), age_f = as.factor(age_f))

fs <- fitted_samples(gn.ice.gam, data = pred.df, n = 1000, seed = 1024,
                       exclude = c('s(lake_id)',  's(year_f)')) |>
    left_join(pred.df |> select(row, ice_off_anomaly, age_f), 
              by = join_by(row == row)) %>%
    drop_na() %>% 
  mutate(age_f = as.factor(age_f),
         group = as.numeric(str_c(age_f, draw)))

fv <- fitted_values(gn.ice.gam, data = pred.df)

fv %>% 
  ggplot(aes(x = ice_off_anomaly, y = fitted, group = age_f)) +
  #geom_ribbon(aes(ymin = lower, ymax = upper, fill = age_f), alpha = 0.1) +
  geom_line(data = fv, aes(x = ice_off_anomaly, y = fitted, group = age_f, colour = age_f)) + 
  labs(color = 'Fish age', fill = 'Fish age' , 
       x ="Ice-Off anomaly", y = "Fitted values") +
  theme(axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.title = element_text(size = 14), 
        legend.text = element_text(size = 12)
        ) + theme_classic()

fig <- fs %>%
  ggplot(aes(x = ice_off_anomaly, y = fitted, group = group)) +
  #geom_ribbon(aes(ymin = lower, ymax = upper, fill = age_f), alpha = 0.1) +
  geom_line(data = fv, aes(x = ice_off_anomaly, y = fitted, 
                           group = age_f, colour = age_f), size = 1.5) + 
  geom_line(aes(colour = age_f), alpha = 0.001) + 
  labs(color = 'Estimated\nage', fill = 'Estimated\nage' , 
       x ="Ice-off Anomaly", y = "Age-class Specific Recruitment") +
  theme_classic() +
  theme(axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18),
        legend.title = element_text(size = 16), 
        legend.text = element_text(size = 14)) + 
  scale_color_brewer(palette = "BrBG") + 
  scale_x_continuous(breaks = c(-15, -10, -5, 0, 5, 10, 15))
fig
write_rds(fig, "./figures/fig3C.rds")
# Figure 3C
ggsave("./figures/Figure3C.jpeg", width = 10, height = 10)
```

# Combine to make figure 3
```{r}
walleye_file <- image_read("./figures/walleye_processed.png")
eggs_file <- image_read("./figures/fish_eggs.png")

fig3A_nowalleye <- readRDS("./figures/fig3A.rds") + labs(x = "")
fig3B_nowalleye <- readRDS("./figures/fig3B.rds") + labs(x = "")
fig3C_nowalleye <- readRDS("./figures/fig3C.rds")



fig3A <- fig3A_nowalleye + 
  coord_cartesian(expand = FALSE, xlim = c(-18, NA), ylim = c(103, NA))+
  annotation_raster(as.raster(walleye_file), 
                    xmin = -18, xmax = -7, ymin = 120, ymax = 127) + 
  annotation_raster(as.raster(eggs_file), 
                    xmin = -11, xmax = -8, ymin = 118, ymax = 121) 
fig3A

fig3B <- fig3B_nowalleye +
  coord_cartesian(expand = FALSE, xlim = c(-18, NA), ylim = c(0, 63))+
  annotation_raster(as.raster(walleye_file), 
                    xmin = -18, xmax = -13, ymin = 57, ymax = 62) +
  annotation_raster(as.raster(walleye_file), 
                  xmin = -18, xmax = -13, ymin = 51.5, ymax = 56.5) +
  annotation_raster(as.raster(walleye_file), 
                    xmin = -13, xmax = -8, ymin = 57, ymax = 62) +
  annotation_raster(as.raster(walleye_file), 
                  xmin = -13, xmax = -8, ymin = 51.5, ymax = 56.5)


fig3C <-
  fig3C_nowalleye + ylim(c(0, 5.4)) + #xlim(-17, 16) +
  coord_cartesian(expand = FALSE, xlim = c(-18, NA), ylim = c(0, 5.75))+
  annotation_raster(as.raster(walleye_file), 
                    xmin = -18, xmax = -8, ymax = 5.6, ymin = 4.6)

fig3B

plot_grid(fig3A, fig3B, fig3C, labels = "auto", ncol = 1)
ggsave("./figures/Figure3.jpeg", height = 14, width = 8)
```


# Plot global smooth for walleye effect
## Not in paper
```{r}
smooth <- smooth_estimates(gn.ice.gam.old)
sm <- smooth %>% 
  #filter(smooth == "s(ice_off_anomaly,age_f)" ) %>%
  #filter(smooth == "s(ice_off_anomaly)" ) %>%
  add_confint() %>%
  add_constant(coef(gn.ice.gam.old)["(Intercept)"]) %>% 
  mutate(upper_ci = upper_ci + coef(gn.ice.gam.old)["(Intercept)"],
         lower_ci = lower_ci + coef(gn.ice.gam.old)["(Intercept)"]) %>%
  transform_fun(inv_link(gn.ice.gam.old))
  
temp_residuals <- gn.ice.gam.old$model %>% 
  add_partial_residuals(gn.ice.gam.old) %>%
  add_constant(coef(gn.ice.gam.old)["(Intercept)"], column = 12) %>%
  transform_fun(inv_link(gn.ice.gam.old), column = 12)

sm %>% filter(smooth == "s(ice_off_anomaly)" ) %>%
    ggplot(aes(x = ice_off_anomaly, y = est, group = age_f)) +
    geom_point(aes(x = ice_off_anomaly, y = `s(ice_off_anomaly)`), 
               alpha = 0.1,
               data = temp_residuals) +
    geom_line(lwd = 1.5) +
    geom_ribbon(aes(ymin = lower_ci , ymax = upper_ci), alpha = 0.3) +
    theme_classic() +
    labs(y = "Age class specific \nwalleye abundance", x = "Ice-Off Anomaly", color = "Age") +
    theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 16)) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 2.1))
```


# Decreases in recruitment to age-6
```{r}
age = 6

data_to_predict <- walleye_anomaly_ice %>% 
  select(est.age, ice_off_anomaly, jd, log_acres, x, y, total.effort.1) %>%
  summarize(across(everything(), ~median(.x, na.rm = T)))



newd <- data.frame(ice_off_anomaly = c(-17.52, 0, 14), acres = data_to_predict$log_acres,
                   x = data_to_predict$x, y = data_to_predict$y, 
                   age_f = age, jd = data_to_predict$jd, 
                   total.effort.1 = data_to_predict$total.effort.1, 
                   lake.id = "40011700", year_f = 2010)
  
predicted = predict(gn.ice.gam.old, newd, type = "response", 
                exclude = c("s(lake.id)", "s(year_f)"))
  
Xp <- predict(gn.ice.gam.old, newd, type = "lpmatrix", 
                exclude = c("s(lake.id)", "s(year_f)") )
  
br <- rmvn(1000, coef(gn.ice.gam.old), gn.ice.gam.old$Vp) ## 1000 replicate param. vectors 
  
early.ice.off <- rep(0, 1000)
normal.ice.off <- rep(0, 1000)
late.ice.off <- rep(0, 1000)
percent.early.normal <- rep(0, 1000)
percent.early.late <- rep(0, 1000)
diff.early.normal <- rep(0,1000)
diff.early.late <- rep(0,1000)

  
for (i in 1:1000) { 
  pr <- Xp %*% br[i,] ## replicate predictions 
  early.ice.off[i] = exp(pr[1,])
  normal.ice.off[i] =  exp(pr[2,]) 
  late.ice.off[i] =  exp(pr[3,])
  percent.early.normal[i] = 1 - (early.ice.off[i]/normal.ice.off[i])
  percent.early.late[i] = 1 - (early.ice.off[i]/late.ice.off[i])
  diff.early.normal[i] <- early.ice.off[i] - normal.ice.off[i]
  diff.early.late[i] <- early.ice.off[i] - late.ice.off[i]
} 

# Early ice-off recruitment to age-4
median(early.ice.off)
quantile(early.ice.off, na.rm = T, probs = c(0.025, 0.975))
         
# Normal ice-off recruitment to age-4
median(normal.ice.off) 
quantile(normal.ice.off, na.rm = T, probs = c(0.025, 0.975))

# Late ice-off recruitment to age-4
median(late.ice.off)
quantile(late.ice.off, na.rm = T, probs = c(0.025, 0.975))
                
                 
# Percent decrease in recruitment from early to normal ice-off (pos = increase)
median(percent.early.normal)*100 # 13.7 % less fish
quantile(percent.early.normal, na.rm = T, probs = c(0.025, 0.975))*100


# Percent decrease in recruitment from early to late ice-off (pos = increase)
median(percent.early.late)*100 # 19.9 % less fish
quantile(percent.early.late, na.rm = T, probs = c(0.025, 0.975))*100

                                 
median(1 - (early.ice.off/late.ice.off), na.rm = T)*100
quantile(1 - (early.ice.off/late.ice.off), na.rm = T, probs = c(0.025, 0.975))*100
                                 
median(early.ice.off - normal.ice.off, na.rm = T) 
quantile(early.ice.off - normal.ice.off, na.rm = T, probs = c(0.025, 0.975))
                                 
median(early.ice.off - late.ice.off, na.rm = T)
quantile(early.ice.off - late.ice.off, na.rm = T, probs = c(0.025, 0.975))
```



#######NEW SECTION########

# Lake specific ice off anomalies
```{r}
long_ice_off <- ice_off %>% filter(DOW %in% long_ice$DOW)

mean_ice <- long_ice_off %>% group_by(DOW) %>% 
  dplyr::filter(year < 1980) %>%
  summarise(mean_ice_off = mean(min_ice_off_julian))

long_ice_anomaly = merge(x = mean_ice, y = long_ice_off, by = "DOW", all.x = T) %>%
  mutate(ice_off_anomaly = max_ice_off_julian - mean_ice_off,
         lake.id = mnsentinellakes::fixlakeid(DOW)) %>% 
  filter(year > 1980) %>% 
  dplyr::select(lake.id, year, max_ice_off_julian, ice_off_anomaly)

walleye_anomaly_ice_lake_specific <- gn_spatial %>%
  merge(y = long_ice_anomaly, by.x = c("lake.id", "birth.year"), by.y = c("lake.id", "year")) %>%
  mutate(log_acres = log(acres), 
         lake.id = as.factor(as.character(lake.id)),
         year_f = as.factor(as.character(year_f)),
         non.fry = ifelse(is.na(non.fry), 0, non.fry),
         age_f = as.factor(est.age)) %>%
  select(lake.id, lake.name,  year, birth.year, est.age, sampling.method, 
         total.effort.1, count, cpue, 
         ice_off_anomaly, x, y, log_acres, shore_mi, non.fry, year_f, jd, effort.ident, age_f) %>% 
  filter(est.age >= 2) %>%
  filter(est.age < 13) %>%
  filter(non.fry <= 1)

# Negative = early ice off
with(walleye_anomaly_ice_lake_specific, hist(x = ice_off_anomaly))

length(unique(walleye_anomaly_ice_lake_specific$lake.id))
range(walleye_anomaly_ice_lake_specific$year)
```


# Model walleye year classes by ice in first year with lake specific ice
```{r}
gn.ice.gam.lake.specific <- gam(count ~ s(ice_off_anomaly) + s(ice_off_anomaly, age_f, bs = "fs") + s(jd) + 
                                  s(log_acres) + s(x, y) +
                    s(lake.id, bs = "re") + s(year_f, bs = "re") + offset(log(total.effort.1)), 
                  family = nb(link = "log"), select = T, method = "REML", 
                  data = walleye_anomaly_ice_lake_specific)

#write_rds(gn.ice.gam.lake.specific, "./models/gillnet.recruitment.anomaly.lakespecific.gam.rds")
#
gn.ice.gam.lake.specific <- read_rds("./models/gillnet.recruitment.anomaly.lakespecific.gam.rds")

gratia::appraise(gn.ice.gam.lake.specific)
k.check(gn.ice.gam.lake.specific)
summary(gn.ice.gam.lake.specific)
gratia::draw(gn.ice.gam.lake.specific, select =1)
#rm(gn.ice.gam.lake.specific)
```


# Plot lake specific ice anomalies
# Figure S4
```{r}
smooth <- smooth_estimates(gn.ice.gam.lake.specific)
sm <- smooth %>%
  filter(smooth == "s(ice_off_anomaly)") %>%
  add_constant(coef(gn.ice.gam.lake.specific)[1]) %>% 
  add_confint()  %>%
  transform_fun(inv_link(gn.ice.gam.lake.specific)) 
  
temp_residuals <- gn.ice.gam.lake.specific$model %>% 
  add_partial_residuals(gn.ice.gam.lake.specific) %>%
  add_constant(coef(gn.ice.gam.lake.specific)[1], column = 12) %>%
  transform_fun(inv_link(gn.ice.gam.lake.specific), column = 12)
  
fig <- sm %>% filter(smooth == "s(ice_off_anomaly)" ) %>%
    ggplot(aes(x = ice_off_anomaly, y = est)) +
    geom_point(aes(x = ice_off_anomaly, y = `s(ice_off_anomaly)`), 
               alpha = 0.1,
               data = temp_residuals) +
    geom_line(lwd = 1.5) +
    geom_ribbon(aes(ymin = lower_ci , ymax = upper_ci), alpha = 0.3) +
    theme_classic() +
    labs(y = "Age class specific \nwalleye recruitment", x = "Ice-Off Anomaly") +
    theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 16)) +
  ylim(0, 2.5)
fig
# Figure S4
ggsave("./figures/FigureS4.jpeg", width = 10, height = 10)
```


# Decreases in recruitment to age-6
## lake specific
```{r}
age = 6


data_to_predict <- walleye_anomaly_ice_lake_specific %>% 
  select(est.age, ice_off_anomaly, jd, log_acres, x, y, total.effort.1) %>%
  summarize(across(everything(), ~median(.x, na.rm = T)))



newd <- data.frame(ice_off_anomaly = c(-17.52, 0, 14), log_acres = data_to_predict$log_acres,
                   x = data_to_predict$x, y = data_to_predict$y, 
                   age_f = age, jd = data_to_predict$jd, 
                   total.effort.1 = data_to_predict$total.effort.1, 
                   lake.id = "40011700", year_f = 2010)
  
predicted = predict(gn.ice.gam.lake.specific, newd, type = "response", 
                exclude = c("s(lake.id)", "s(year_f)"))
  
Xp <- predict(gn.ice.gam.lake.specific, newd, type = "lpmatrix", 
                exclude = c("s(lake.id)", "s(year_f)") )
  
br <- rmvn(1000, coef(gn.ice.gam.lake.specific), gn.ice.gam.lake.specific$Vp) ## 1000 replicate param. vectors 
  
early.ice.off <- rep(0, 1000)
normal.ice.off <- rep(0, 1000)
late.ice.off <- rep(0, 1000)
percent.early.normal <- rep(0, 1000)
percent.early.late <- rep(0, 1000)
diff.early.normal <- rep(0,1000)
diff.early.late <- rep(0,1000)

  
for (i in 1:1000) { 
  pr <- Xp %*% br[i,] ## replicate predictions 
  early.ice.off[i] = exp(pr[1,])
  normal.ice.off[i] =  exp(pr[2,]) 
  late.ice.off[i] =  exp(pr[3,])
  percent.early.normal[i] = 1 - (early.ice.off[i]/normal.ice.off[i])
  percent.early.late[i] = 1 - (early.ice.off[i]/late.ice.off[i])
  diff.early.normal[i] <- early.ice.off[i] - normal.ice.off[i]
  diff.early.late[i] <- early.ice.off[i] - late.ice.off[i]
} 

# Early ice-off recruitment to age-4
median(early.ice.off)
quantile(early.ice.off, na.rm = T, probs = c(0.025, 0.975))
         
# Normal ice-off recruitment to age-4
median(normal.ice.off) 
quantile(normal.ice.off, na.rm = T, probs = c(0.025, 0.975))

# Late ice-off recruitment to age-4
median(late.ice.off)
quantile(late.ice.off, na.rm = T, probs = c(0.025, 0.975))
                
                 
# Percent decrease in recruitment from early to normal ice-off (pos = increase)
median(percent.early.normal)*100 # 13.7 % less fish
quantile(percent.early.normal, na.rm = T, probs = c(0.025, 0.975))*100


# Percent decrease in recruitment from early to late ice-off (pos = increase)
median(percent.early.late)*100 # 19.9 % less fish
quantile(percent.early.late, na.rm = T, probs = c(0.025, 0.975))*100

                                 
median(1 - (early.ice.off/late.ice.off), na.rm = T)*100
quantile(1 - (early.ice.off/late.ice.off), na.rm = T, probs = c(0.025, 0.975))*100
                                 
median(early.ice.off - normal.ice.off, na.rm = T) 
quantile(early.ice.off - normal.ice.off, na.rm = T, probs = c(0.025, 0.975))
                                 
median(early.ice.off - late.ice.off, na.rm = T)
quantile(early.ice.off - late.ice.off, na.rm = T, probs = c(0.025, 0.975))
```


# Map
```{r}
mn_state <- map_data("state", "Minnesota")
mn_counties <- map_data("county", "Minnesota")

plot_ids_age <- walleye_anomaly_ice %>% 
  group_by(lake.id, year, total.effort.1) %>% count()

plot_ids <- plot_ids_age %>% 
  group_by(lake.id) %>% count() %>% filter(n > 4)
sum(plot_ids$n)

walleye_anomaly_ice %>% 
  filter(lake.id %in% plot_ids$lake.id) %>%
  group_by(lake.id) %>%
  summarise(n = n(), 
            lat = unique(y),
            long = unique(x)) %>%
  ggplot() + 
  geom_polygon(data = mn_state, 
               aes(x = long, y = lat, group = group), 
               colour="black", fill="NA", lwd=1 )  + 
  geom_polygon(data = mn_counties, aes(x = long, y = lat, group = group), 
               alpha = 0.5, fill = "white", color = "black") +
  coord_fixed(1.3) +
  geom_point(aes(x = long, y = lat, size = n), 
             pch = 21, alpha = 0.5, color = "black", fill = "black") +
  scale_size_continuous(breaks = c(6, 15, 25)) +
  theme(plot.title = element_text(hjust = 0.5, size = 18),
        plot.subtitle = element_text(hjust = 0.5),
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) + 
  theme(legend.position = c(.85, 0.38)) + 
  labs(size = "Number of \nGN surveys",
       x = "Longitude", y = "Latitude")
#ggsave("./figures/gn_surveys.jpeg", width = 7, height = 7)
```
